Iconic representations of molluscs through the ages

### 2012-10-26 large_number_squeezing_with_atoms.tex
More appendix. Everyone likes appendix.

Beginning with the Hamiltonian $H_3$, during the period $(t_2, t_3)$ mode $|a\rangle$ will evolve as
\begin{equation}
\hat{a}_3 = e^{ i H_3 t/ \hbar} \, \hat{a}_2 \, e^{-i H_3 t/ \hbar}.
\end{equation}
Utilizing the Hadamard lemma
\begin{equation}
e^X Y e^{-X} = Y + [X,Y] + \frac{1}{2!}[X,[X,Y]] + \frac{1}{3!}[X,[X,[X,Y]]] + \ldots
\end{equation}
we obtain
\begin{eqnarray}
\hat{a}_3 &=& \hat{a}_2 - i e^{i\phi} \Omega \tau \hat{b}_2 + \frac{(i \Omega \tau)^2}{2!} \hat{a}_2 - \frac{(i \Omega \tau)^3}{3!}e^{i\phi} \hat{b}_2 + \frac{(i \Omega \tau)^4}{4!} \hat{a}_2 - \ldots \nonumber \\
          &=& \cos (\Omega \tau) \hat{a}_2 -i e^{i\phi} \sin (\Omega\tau) \hat{b}_2
\end{eqnarray}
where $\tau=t_3-t_2$ is the period for which the coupling is applied. Similarly, we find
\begin{equation}
\hat{b}_3 = \cos (\Omega \tau) \hat{b}_2 -i e^{-i\phi} \sin (\Omega\tau) \hat{a}_2.
\end{equation}

(1) Find $\hat{a}_2$, $\hat{a}_2$ in terms of $\hat{a}_1$, $\hat{b}_1$.

(2) Derive 1631.5 and explain we need expectation values of the bilinear, trilinear and quartic terms. We can use result of previous step to do them, provided we normally order everything

(3) Take each set of terms from 1631.5 individually, normal order them, and evaluate

(4) Plug list of expectation values back into 1631.5

\begin{eqnarray}
s &=& \sin(\Omega (t_3 - t_2)) \\
c &=& \cos(\Omega (t_3 - t_2)) \\
\lambda_{ij} &=& \chi_{ij} \tau_{\mathrm{hold}} / \hbar \\
A &=& \sqrt{n_a} \exp [n_a (e^{-i(\lambda_{aa}-\lambda_{ab})} - 1 )] \\
A_2 &=& n_a \exp [n_a (e^{-2i(\lambda_{aa}-\lambda_{ab})} - 1 )] \\
B &=& -i e^{i \phi}\sqrt{n_b} \exp [n_b (e^{-i(\lambda_{bb}-\lambda_{ab})} - 1 )] \\
B_2 &=& -n_b e^{2i\phi} \exp [n_b (e^{-2i(\lambda_{bb}-\lambda_{ab})} - 1 )]
\end{eqnarray}
then the expectation values for number and number squared at time $t=t_3$ are given by
\begin{eqnarray}
\langle \hat{a}^{\dagger}(t_3) \hat{a}(t_3) \rangle &=& n_a c^2 + n_b s^2 + i c s (A B^* - A^* B) \\
%
\langle \hat{b}^{\dagger}(t_3) \hat{b}(t_3) \rangle &=& n_a s^2 + n_b c^2 - i c s (A B^* - A^* B) \\
%
\langle \hat{a}^{\dagger}(t_3) \hat{a}(t_3) \hat{a}^{\dagger}(t_3)  \hat{a}(t_3) \rangle &=& (n_a^2 + n_a) c^4 + (n_b^2 + n_b) s^4 \nonumber \\
&& + c^2 s^2 [n_a +n_b +4 n_a n_b - e^{i(\lambda_{aa}-\lambda_{bb})} B_2 A_2^* - e^{-i(\lambda_{aa}-\lambda_{bb})} B_2^* A_2] \nonumber \\
&& + i c^3 s [2 n_a e^{-i(\lambda_{aa}-\lambda_{ab})}] A B^* - 2 n_a e^{i(\lambda_{aa}-\lambda_{ab})} A^* B + A B^* - A^* B] \nonumber \\
&& + i c s^3 [2 n_b e^{i(\lambda_{bb}-\lambda_{ab})}] A B^* - 2 n_b e^{-i(\lambda_{bb}-\lambda_{ab})} A^* B + A B^* - A^* B] \\
%
\langle \hat{b}^{\dagger}(t_3)  \hat{b}(t_3) \hat{b}^{\dagger}(t_3)  \hat{b}(t_3) \rangle &=& (n_b^2 + n_b) c^4 + (n_a^2 + n_a) s^4 \nonumber \\
&& + c^2 s^2 [n_a +n_b +4 n_a n_b - e^{-i(\lambda_{aa}-\lambda_{bb})} B_2^* A_2 - e^{i(\lambda_{aa}-\lambda_{bb})} B_2 A_2^*] \nonumber \\
&& + i c^3 s [2 n_b e^{-i(\lambda_{bb}-\lambda_{ab})}] A^* B - 2 n_b e^{i(\lambda_{bb}-\lambda_{ab})} A B^* - A^* B + A B^*] \nonumber \\
&& + i c s^3 [2 n_a e^{i(\lambda_{aa}-\lambda_{ab})}] A^* B - 2 n_a e^{-i(\lambda_{aa}-\lambda_{ab})} A B^* - A^* B + A B^*] 
\end{eqnarray}

@@

\section*{References}
\begin{thebibliography}{10}
\bibitem{gross2010} Gross C, Zibold T, Est{\`{e}}ve J and Oberthaler M K 2010 Nonlinear atom interferometer surpasses classical
precision limit {\it Nature} {\bf 464} 1165--1169
\bibitem{dennis2013} Dennis G R, Hope J J and Johnsson M T 2013 XMDS2: Fast, scalable simulation of coupled stochastic partial
differential equations {\it Comput. Phys. Commun.} {\bf 184} 201--208

\end{thebibliography}

>>>>

Beginning with the Hamiltonian $H_1$, during the period $(0, t_1)$ mode $\hat{a}$ will evolve as
\begin{equation}
\hat{a}_1 = e^{ i H_1 t/ \hbar} \, \hat{a}_0 \, e^{-i H_1 t/ \hbar}.
\end{equation}
Utilizing the Hadamard lemma
\begin{equation}
e^X Y e^{-X} = Y + [X,Y] + \frac{1}{2!}[X,[X,Y]] + \frac{1}{3!}[X,[X,[X,Y]]] + \ldots
\label{eqHadamard}
\end{equation}
we obtain 
\begin{eqnarray}
\hat{a}_1 &=& \hat{a}_0 - i \Omega t_1 \hat{b}_0 + \frac{(i \Omega t_1)^2}{2!} \hat{a}_0 - \frac{(i \Omega t_1)^3}{3!} \hat{b}_0 + \frac{(i \Omega t_1)^4}{4!} \hat{a}_2 - \ldots \nonumber \\
          &=& \cos (\Omega t_1) \hat{a}_0 -i \sin (\Omega t_1) \hat{b}_0
\label{eqa1}
\end{eqnarray}
Similarly, we find
\begin{equation}
\hat{b}_1 = \cos (\Omega t_1) \hat{b}_0 - i \sin (\Omega t_1) \hat{a}_0.
\label{eqb1}
\end{equation}
From the form of (\ref{eqa1}) and (\ref{eqb1}) it is clear that as both modes $\hat{a}$ and $\hat{b}$ began in coherent states, they will remain in coherent states, with only their amplitudes changing. Specifically, at time $t_1$ the system is in a product of coherent states, which we denote $|\alpha, \beta\rangle$ with $\alpha=\sqrt{n_a}$ and $\beta=-i\sqrt{n_b}$.

Next we consider evolution under $H_2$. Taking mode $\hat{a}$ first, we note that as it commutes with the $\hat{b}^{\dagger} \hat{b}^{\dagger} \hat{b} \hat{b}$ term, and since $\hat{a}^{\dagger} \hat{a}^{\dagger} \hat{a} \hat{a}$ commutes with $\hat{a}^{\dagger} \hat{a} \hat{b}^{\dagger} \hat{b}$ we have
\begin{equation}
\hat{a}_2 = e^{i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1 \hat{b}_1^{\dagger} \hat{b}_1 } 
          e^{ i \frac{\lambda_{aa}} {2} \hat{a}_1^{\dagger} \hat{a}_1^{\dagger} \hat{a}_1 \hat{a}_1}\, \hat{a}_1 \,  
          e^{ -i \frac{\lambda_{aa}}{2} \hat{a}_1^{\dagger} \hat {a}_1^{\dagger} \hat{a}_1 \hat{a}_1 }
          e^{-i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1 \hat{b}_1^{\dagger} \hat{b}_1}.
\label{eqa2evolution}
\end{equation}
where we have defined $\lambda_{ij} = \chi_{ij} (t_2-t_1)/\hbar$. Utilizing (\ref{eqHadamard}) to move $\hat{a}_1$ through the exponential, with some algebra one can show that
\begin{eqnarray}
e^{ i \frac{\lambda_{aa}} {2} \hat{a}_1^{\dagger} \hat{a}_1^{\dagger} \hat{a}_1 \hat{a}_1} \hat{a}_1 
         e^{ -i \frac{\lambda_{aa}} {2} \hat{a}_1^{\dagger} \hat{a}_1^{\dagger} \hat{a}_1 \hat{a}_1} &=& \left[ \sum_{n=0} (-i \lambda_{aa})^n (\hat{a}_1^{\dagger} \hat{a}_1)^n \right] \hat{a}_1 \nonumber \nonumber \\
   &=& \exp[-i \lambda_{aa} \hat{a}_1^{\dagger} \hat{a}_1] \hat{a}_1
\end{eqnarray}
To handle the cross-nonlinearity term in (\ref{eqa2evolution}) we use the identity \cite{louisell}
\begin{equation}
e^{x \hat{a}^{\dagger} \hat{a}} f(\hat{a}, \hat{a}^{\dagger}) e^{-x \hat{a}^{\dagger} \hat{a}} = f(\hat{a}e^{-x}, \hat{a}^{\dagger} e^{x})
\label{eqefeidentity}
\end{equation}
to obtain
\begin{eqnarray}
\hat{a}_2 &=& e^{i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1 \hat{b}_1^{\dagger} \hat{b}_1 } 
          e^{-i \lambda_{aa} \hat{a}_1^{\dagger} \hat{a}_1} \, \hat{a}_1 \,
          e^{-i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1 \hat{b}_1^{\dagger} \hat{b}_1} \nonumber \\
%
          &=& e^{-i \lambda_{aa} \hat{a}_1^{\dagger} \hat{a}_1} 
              e^{i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1 \hat{b}_1^{\dagger} \hat{b}_1 } \, \hat{a}_1 \,
          e^{-i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1 \hat{b}_1^{\dagger} \hat{b}_1} \nonumber \\
%
          &=& e^{-i \lambda_{aa} \hat{a}_1^{\dagger} \hat{a}_1} e^{-i \lambda_{ab} \hat{b}_1^{\dagger} \hat{b}_1} \, \hat{a}_1
\label{eqa2}
\end{eqnarray}
Similarly, from permutation symmetry, we have
\begin{equation}
\hat{b}_2 = e^{-i \lambda_{bb} \hat{b}_1^{\dagger} \hat{b}_1} e^{-i \lambda_{ab} \hat{a}_1^{\dagger} \hat{a}_1} \, \hat{b}_1.     
\label{eqb2}
\end{equation}
Finally, to obtain $\hat{a}_3$ and $\hat{b}_3$ we utilize (\ref{eqa1}) and (\ref{eqb1}) with the phase factor attached to the $\hat{b}$ operator to obtain
\begin{eqnarray}
\hat{a}_3 &=& \cos (\Omega (t_3-t_2)) \hat{a}_2 -i e^{i\phi} \sin (\Omega (t_3-t_2)) \hat{b}_2 \label{eqa3} \\
\hat{b}_3 &=& \cos (\Omega (t_3-t_2)) \hat{b}_2 - i e^{-i\phi} \sin (\Omega (t_3-t_2)) \hat{a}_2 \label{eqb3}
\end{eqnarray} 
We are now in a position to evaluate the number variance of the system throughout period of the final coupling. We first consider the number variance of the $\hat{a}$ field, which is defined as
\begin{equation}
{\mathrm{Var}}[N_a] = \langle \hat{a}^{\dagger}_3 \hat{a}_3 \hat{a}^{\dagger}_3 \hat{a}_3 \rangle - \langle \hat{a}^{\dagger}_3 \hat{a}_3 \rangle ^2.
\label{eqNavariance}
\end{equation}
Making use of (\ref{eqa3}) and using the shorthand notation 
\begin{eqnarray}
s &=& \sin[\Omega (t_3 - t_2)] \\
c &=& \cos[\Omega (t_3 - t_2)]
\end{eqnarray}
we have
\begin{eqnarray}
\hat{a}^{\dagger}_3 \hat{a}_3 &=& \hat{a}^{\dagger}_2 \hat{a}_2 c^2 +  \hat{b}^{\dagger}_2 \hat{b}_2 s^2 + i c s e^{-i \phi} \hat{b}^{\dagger}_2 \hat{a}_2 - i c s e^{i \phi} \hat{a}^{\dagger}_2 \hat{b}_2 \\
%
\hat{a}^{\dagger}_3 \hat{a}_3 \hat{a}^{\dagger}_3 \hat{a}_3 &=& \hat{a}^{\dagger}_2 \hat{a}_2 \hat{a}^{\dagger}_2 \hat{a}_2 c^4 + \hat{b}^{\dagger}_2 \hat{b}_2 \hat{b}^{\dagger}_2 \hat{b}_2 s^4 \nonumber \\
%
&& + c^2 s^2 [ \hat{a}^{\dagger}_2 \hat{a}_2 + \hat{b}^{\dagger}_2 \hat{b}_2 + 4 \hat{a}^{\dagger}_2 \hat{a}_2 \hat{b}^{\dagger}_2 \hat{b}_2 -e^{-2 i \phi} \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 -e^{-2 i \phi} \hat{b}^{\dagger}_2 \hat{b}^{\dagger}_2 \hat{a}_2 \hat{a}_2 ] \nonumber \\
%
&& + i c^3 s [2 e^{-i \phi} \hat{b}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{a}_2 \hat{a}_2 - 2 e^{i \phi} \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{a}_2 \hat{b}_2 + e^{-i \phi} \hat{b}^{\dagger}_2 \hat{a}_2 - e^{i \phi} \hat{a}^{\dagger}_2 \hat{b}_2 ] \nonumber \\
%
&& + i c s^3 [2 e^{-i \phi} \hat{b}^{\dagger}_2 \hat{b}^{\dagger}_2 \hat{a}_2 \hat{b}_2 - 2 e^{i \phi} \hat{a}^{\dagger}_2 \hat{b}^{\dagger}_2 \hat{b}_2 \hat{b}_2 + e^{-i \phi} \hat{b}^{\dagger}_2 \hat{a}_2 - e^{i \phi} \hat{a}^{\dagger}_2 \hat{b}_2 ] 
\end{eqnarray}
Clearly, to calculate (\ref{eqNavariance}) we will need the expectation values of terms quartic and quadratic in $\hat{a}_2$ and ${\hat{b}_2}$. Specifically, we require $\langle \hat{a}^{\dagger}_2 \hat{a}_2 \rangle$, $\langle \hat{b}^{\dagger}_2 \hat{b}_2 \rangle$,  $\langle \hat{a}^{\dagger}_2 \hat{b}_2 \rangle$, $\langle \hat{a}^{\dagger}_2 \hat{a}_2 \hat{a}^{\dagger}_2 \hat{a}_2 \rangle$, $\langle \hat{b}^{\dagger}_2 \hat{b}_2 \hat{b}^{\dagger}_2 \hat{b}_2 \rangle$ , $\langle \hat{a}^{\dagger}_2 \hat{a}_2 \hat{b}^{\dagger}_2 \hat{b}_2 \rangle$, $\langle \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 \rangle$, $\langle \hat{a}^{\dagger}_2 \hat{b}^{\dagger}_2 \hat{a}_2 \hat{a}_2 \rangle$, and $\langle \hat{a}^{\dagger}_2 \hat{b}^{\dagger}_2 \hat{b}_2 \hat{b}_2 \rangle$, as well as their Hermitian conjugates.

As $\hat{a}^{\dagger}_1 \hat{a}_1$ and $\hat{b}^{\dagger}_1 \hat{b}_1$ commute with the Hamiltonian $H_2$, they are constants of motion so we have
\begin{equation}
\langle \hat{a}^{\dagger}_2 \hat{a}_2 \rangle = \langle \hat{a}^{\dagger}_1 \hat{a}_1 \rangle = \langle \alpha, \beta | \hat{a}^{\dagger}_1 \hat{a}_1 |\alpha, \beta \rangle = |\alpha|^2 = n_a
\end{equation}
%
\begin{equation}
\langle \hat{b}^{\dagger}_2 \hat{b}_2 \rangle = \langle \hat{b}^{\dagger}_1 \hat{b}_1 \rangle = \langle \alpha, \beta | \hat{b}^{\dagger}_1 \hat{b}_1 |\alpha, \beta \rangle = |\beta|^2 = n_b
\end{equation}
%
\begin{equation}
\langle \hat{a}^{\dagger}_2 \hat{a}_2 \hat{b}^{\dagger}_2 \hat{b}_2 \rangle = \langle \hat{a}^{\dagger}_1 \hat{a}_1 \hat{b}^{\dagger}_1 \hat{b}_1 \rangle = \langle \alpha, \beta | \hat{a}^{\dagger}_1 \hat{a}_1 \hat{b}^{\dagger}_1 \hat{b}_1 |\alpha, \beta \rangle = |\alpha|^2 |\beta|^2 = n_a n_b
\end{equation}
Furthermore, $\hat{a}^{\dagger}_2 \hat{a}_2 \hat{a}^{\dagger}_2 \hat{a}_2$ and $\hat{b}^{\dagger}_2 \hat{b}_2 \hat{b}^{\dagger}_2 \hat{b}_2$ also commute with $H_2$, giving
\begin{equation}
\langle \hat{a}^{\dagger}_2 \hat{a}_2 \hat{a}^{\dagger}_2 \hat{a}_2 \rangle = \langle \hat{a}^{\dagger}_1 \hat{a}_1 \hat{a}^{\dagger}_1 \hat{a}_1 \rangle = \langle \alpha, \beta | \hat{a}^{\dagger}_1 \hat{a}^{\dagger}_1 \hat{a}_1 \hat{a}_1 + \hat{a}^{\dagger}_1 \hat{a}_1 |\alpha, \beta \rangle = n_a^2 + n_a
\end{equation}
%
\begin{equation}
\langle \hat{b}^{\dagger}_2 \hat{b}_2 \hat{b}^{\dagger}_2 \hat{b}_2 \rangle = \langle \hat{b}^{\dagger}_1 \hat{b}_1 \hat{b}^{\dagger}_1 \hat{b}_1 \rangle = \langle \alpha, \beta | \hat{b}^{\dagger}_1 \hat{b}^{\dagger}_1 \hat{b}_1 \hat{b}_1 + \hat{b}^{\dagger}_1 \hat{b}_1 |\alpha, \beta \rangle = n_b^2 + n_b
\end{equation}
The remaining terms are not constants of motion, so we proceed by making use of (\ref{eqa2}) and (\ref{eqb2}). For $\langle \hat{a}^{\dagger}_2 \hat{b}_2 \rangle$ we have
\begin{equation}
\hat{a}^{\dagger}_2 \hat{b}_2 = \hat{a}^{\dagger}_1 e^{-i (\lambda_{bb} - \lambda_{ab}) \hat{b}^{\dagger}_1 \hat{b}_1} e^{i (\lambda_{aa} - \lambda_{ab}) \hat{a}^{\dagger}_1 \hat{a}_1} \hat{b}_1 
\end{equation}
To calculate the expectation value of this expression, the creation and annihilation operators must be normally ordered. Making use of the identity \cite{louisell}
\begin{equation}
e^{x \hat{a}^{\dagger} \hat{a}} = \sum_{n=0}^{\infty} \frac{(e^x - 1)^n} {n!} (\hat{a}^{\dagger})^n (\hat{a})^n
\end{equation}
allows us to compute expectation values of coherent states of the form
\begin{eqnarray}
\langle \alpha | e^{x \hat{a}^{\dagger} \hat{a}} |\alpha \rangle &=& \sum_{n=0}^{\infty} \frac{(e^x - 1)^n} {n!} |\alpha|^{2n} \nonumber \\
%
&=& \exp[|\alpha|^2(e^x -1)] \label{eqExpectationValueOfExponential}
\end{eqnarray}
This gives
\begin{eqnarray}
\langle \hat{a}^{\dagger}_2 \hat{b}_2 \rangle &=& \langle \alpha, \beta | \hat{a}^{\dagger}_1 e^{-i (\lambda_{bb} - \lambda_{ab}) \hat{b}^{\dagger}_1 \hat{b}_1} e^{i (\lambda_{aa} - \lambda_{ab}) \hat{a}^{\dagger}_1 \hat{a}_1} \hat{b}_1 | \alpha, \beta \rangle \nonumber \\
%
&=& \alpha^* \beta \exp[|\alpha|^2(e^{i (\lambda_{aa} - \lambda_{ab})} -1)] \exp[|\beta|^2 (e^{-i (\lambda_{bb} - \lambda_{ab})} -1)]
\end{eqnarray}

Next we tackle $\langle \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 \rangle$. Using (\ref{eqa2}) and (\ref{eqb2}) and the fact that $\hat{a}$ and $\hat{b}$ commute, we have
\begin{eqnarray}
\hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 &=& \hat{a}^{\dagger}_1 
  e^{i (\lambda_{aa}-\lambda_{ab}) \hat{a}^{\dagger}_1 \hat{a}_1}
  \hat{b}_1 \hat{a}^{\dagger_1}
  e^{i (\lambda_{ab}-\lambda_{bb}) \hat{b}^{\dagger}_1 \hat{b}_1}
  e^{i (\lambda_{aa}-\lambda_{ab}) \hat{a}^{\dagger}_1 \hat{a}_1}
  \hat{b}_1 \\
%
&=& \hat{a}^{\dagger}_1 \hat{a}^{\dagger}_1 
    e^{2i (\lambda_{aa}-\lambda_{ab}) \hat{a}^{\dagger}_1 \hat{a}_1}
    e^{2i (\lambda_{ab}-\lambda_{bb}) \hat{b}^{\dagger}_1 \hat{b}_1}
    \hat{b}_1 \hat{b}_1 e^{i(\lambda_{aa}-\lambda_{bb})}
\end{eqnarray}
where we have made multiple uses of the identity 
\begin{equation}
\hat{a} e^{i x \hat{a}^{\dagger} \hat{a}} = e^{i x \hat{a}^{\dagger} \hat{a}} \hat{a} e^{ix}
\end{equation}
which follows from (\ref{eqefeidentity}). Finally, applying (\ref{eqExpectationValueOfExponential}) we obtain
\begin{equation}
\langle \hat{a}^{\dagger}_2 \hat{a}^{\dagger}_2 \hat{b}_2 \hat{b}_2 \rangle = \alpha^{*2} \beta^2 e^{i(\lambda_{aa}-\lambda_{bb})} \exp[|\alpha|^2(e^{2i (\lambda_{aa} - \lambda_{bb})} -1)] \exp[|\beta|^2(e^{-2i (\lambda_{bb} - \lambda_{bb})} -1)] 
\end{equation}

then the expectation values for number and number squared at time $t=t_3$ are given by
\begin{eqnarray}
\langle \hat{a}^{\dagger}(t_3) \hat{a}(t_3) \rangle &=& n_a c^2 + n_b s^2 + i c s (A B^* - A^* B) \\
%
\langle \hat{b}^{\dagger}(t_3) \hat{b}(t_3) \rangle &=& n_a s^2 + n_b c^2 - i c s (A B^* - A^* B) \\
%
\langle \hat{a}^{\dagger}(t_3) \hat{a}(t_3) \hat{a}^{\dagger}(t_3)  \hat{a}(t_3) \rangle &=& (n_a^2 + n_a) c^4 + (n_b^2 + n_b) s^4 \nonumber \\
&& + c^2 s^2 [n_a +n_b +4 n_a n_b - e^{i(\lambda_{aa}-\lambda_{bb})} B_2 A_2^* - e^{-i(\lambda_{aa}-\lambda_{bb})} B_2^* A_2] \nonumber \\
&& + i c^3 s [2 n_a e^{-i(\lambda_{aa}-\lambda_{ab})}] A B^* - 2 n_a e^{i(\lambda_{aa}-\lambda_{ab})} A^* B + A B^* - A^* B] \nonumber \\
&& + i c s^3 [2 n_b e^{i(\lambda_{bb}-\lambda_{ab})}] A B^* - 2 n_b e^{-i(\lambda_{bb}-\lambda_{ab})} A^* B + A B^* - A^* B] \\
%
\langle \hat{b}^{\dagger}(t_3)  \hat{b}(t_3) \hat{b}^{\dagger}(t_3)  \hat{b}(t_3) \rangle &=& (n_b^2 + n_b) c^4 + (n_a^2 + n_a) s^4 \nonumber \\
&& + c^2 s^2 [n_a +n_b +4 n_a n_b - e^{-i(\lambda_{aa}-\lambda_{bb})} B_2^* A_2 - e^{i(\lambda_{aa}-\lambda_{bb})} B_2 A_2^*] \nonumber \\
&& + i c^3 s [2 n_b e^{-i(\lambda_{bb}-\lambda_{ab})}] A^* B - 2 n_b e^{i(\lambda_{bb}-\lambda_{ab})} A B^* - A^* B + A B^*] \nonumber \\
&& + i c s^3 [2 n_a e^{i(\lambda_{aa}-\lambda_{ab})}] A^* B - 2 n_a e^{-i(\lambda_{aa}-\lambda_{ab})} A B^* - A^* B + A B^*] 
\end{eqnarray}

@@

\section*{References}
\begin{thebibliography}{10}
\bibitem{gross2010} Gross C, Zibold T, Est{\`{e}}ve J and Oberthaler M K 2010 Nonlinear atom interferometer surpasses classical
precision limit {\it Nature} {\bf 464} 1165--1169
\bibitem{dennis2013} Dennis G R, Hope J J and Johnsson M T 2013 XMDS2: Fast, scalable simulation of coupled stochastic partial
differential equations {\it Comput. Phys. Commun.} {\bf 184} 201--208
\bibitem{louisell} Louisell Quantum Statistical Properties of Radiation
\end{thebibliography}
